Carbonate chemistry at Ny-Ålesund

### 2022-08-16 awipev-CO2.Rmd
Added calculation of OmegaAragonite

## Miscellaneous

###Save all

>>>>

## Miscellaneous
### OmegaAragonite
OmegaAragonite is calculated using at_calc and pCO2
```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
# we calculate it from at_calc and pCO2
# nuts are not taken into consideration
tmp <- d_all %>% # just for this chunk
  dplyr::select(datetime, monthd, sal_fb_mix, temp_fb, pco2_fb, at_calc) %>% 
  tidyr::drop_na() %>% 
  dplyr::mutate(OmegaAragonite = seacarb::carb(
    flag = 24, var1 = pco2_fb, var2 = at_calc*1e-6, S=sal_fb_mix, T=temp_fb, 
    Patm=1, P=1.1, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$OmegaAragonite)
#plot
size_point <- 0.3 # size of data points
alpha <- 1 #transparency
size_labs <- 6 # font size labels

ts_oa <- tmp %>%
  ggplot(aes(x = datetime, y = OmegaAragonite), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title="Aragonite saturation state (11 m)",x="", y=latex2exp::TeX("$\\Omega)$")) +
  Mytheme(size_labs = size_labs)
print(ts_oa)
ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 30, units = "cm")
```

### Save all
